\cursedforest\ - A Random Forest Implementation for ``Big'' and ``Wide'' Data \\ Supplementary Information

### 2016-11-17 doc/publications/plos16/plos16.tex
a few table numbers

\multirow{3}{*}{phase1\_chr22: 1,092 x 490,036} & \cursedforest\ & 0.077  &                         \\
                                                & Spark ML  &  Aidan           &           Aidan         \\
                                                & RF - R         & 0.05       & 24 min           \\
                                                & ranger - R      & 0.06       & 1 min 10 seconds       \\
                                                & ranger - c++     & 0.06       & 7 mins            \\

 \hline
\multirow{3}{*}{phase3\_chr22: 2,504 x 1,103,548}   &               &            &                  \\
                                                    & RF - R        & NA         & NA                \\
                                                    & H2O           & 0.05       & 16 hours         \\
                                                    & ranger - R    & 0.06       & 4 1/2 mins     \\
\hline
\multirow{3}{*}{phase3\_chr1: 2,504 x 6,450,364}    & \cursedforest\ & 0.063  & 1hr 58min         \\
                                                    & Spark ML  & 0.94       & 8hr 29min        \\
                                                    & ranger - R      &  0.05       & 28 mins         \\
\hline
\multirow{3}{*}{phase3\_chr1-3: 2,504 x 19,328,051} & \cursedforest\ & 0.046  & 4hr 0min               \\
                                                    & RF - Spark ML  &    Aidan         &   Aidan               \\
                                                    & ranger - R      & 0.03      &         \\
& ranger - R        &             0.973     &      03:58           \\
\hline

\multirow{4}{*}{phase3\_chr1-22: 2,504 x 81,047,467} & \cursedforest\ & XX  & 7hr 14min \\
& Spark ML & Aidan & Aidan  \\
& ranger (C++)       &        NA     &        NA      \\
& ranger (C++)       &        NA     &        NA    \\
\hline
\end{tabular}
\begin{flushleft} 
Comparison of different various machine learning libraries on different subsets of variant data 
from the 1000 Genomes Project.
Each random forest model consists of 50 trees.
\end{flushleft}
\label{table1}
%\end{adjustwidth}
\end{minipage}
\end{table}

>>>>

\multirow{3}{*}{phase1\_chr22: 1,092 x 490,036} & \cursedforest\ & 0.04  & 1 min 50 seconds                        \\
                                                & RF - Spark ML  &  Aidan           &           Aidan         \\
                                                & RF - R         & 0.05       & 24 min           \\
                                                & ranger - R      & 0.06       & 1 min 10 seconds       \\
                                                & ranger - c++     & 0.06       & 7 mins            \\

 \hline
\multirow{3}{*}{phase3\_chr22: 2,504 x 1,103,548}   &               &            &                  \\
                                                    & RF - R        & NA         & NA                \\
                                                    & H2O           & 0.05       & 16 hours         \\
                                                    & ranger - R    & 0.06       & 4 min 30 seconds     \\
\hline
\multirow{3}{*}{phase3\_chr1: 2,504 x 6,450,364}    & \cursedforest\ & 0.063  & 1hr 58min         \\
                                                    & RF - Spark ML  & 0.04       & 8hr 29min        \\
                                                    & ranger - R      &  0.05       & 28 mins         \\
\hline
\multirow{3}{*}{phase3\_chr1-3: 2,504 x 19,328,051} & \cursedforest\ & 0.046  & 4hr 0min               \\
                                                    & RF - Spark ML  &    NA         &   NA               \\
                                                    & ranger - R      & 0.03      &         \\
& ranger - R        &             0.973     &      03:58           \\
\hline

\multirow{4}{*}{phase3\_chr1-22: 2,504 x 81,047,467} & \cursedforest\ & XX  & 7hr 14min \\
& Spark ML & NA & NA  \\
& ranger (C++)       &        NA     &        NA      \\
& ranger (C++)       &        NA     &        NA    \\
\hline
\end{tabular}
\begin{flushleft} 
Comparison of different various machine learning libraries on different subsets of variant data 
from the 1000 Genomes Project.
Each random forest model consists of 50 trees.
\end{flushleft}
\label{table1}
%\end{adjustwidth}
\end{minipage}
\end{table}
